---
title: "p8105_hw1"
author: "Yue Gu"
date: 2018-09-16
output: github_document
---


# Library
```{r, message = FALSE}
library(tidyverse)
```

# Problem 1

## Creating data frame
Here's a random sample of size 10 from a uniform[0,5] distribution,
and I created logical vector, character vector and factor vector as required.


```{r}
Prob1_df = tibble(
  vec_numeric = runif(10, min = 0, max = 5),
  vec_logical = c(vec_numeric > 2),
  vec_char = c("I", "am", "happy", "to", "take", "the", "data", "science", "course", "today"),
  vec_factor = factor(c("T", "F", "T", "F", "T", "F", "T", "T", "F", "F"))
)
```


Examine classes:
```{r}
class(Prob1_df$vec_numeric)
class(Prob1_df$vec_logical)
class(Prob1_df$vec_char)
class(Prob1_df$vec_factor)
```

Length of the vector shown below:
```{r}
length(Prob1_df$vec_char)
length(Prob1_df$vec_factor)
```


## Take means
```{r}
mean(Prob1_df$vec_numeric)
mean(Prob1_df$vec_logical)
mean(Prob1_df$vec_char)
mean(Prob1_df$vec_factor)
```
When taking the mean of each variable, only vec_numeric works since it's the only numerical variable that could have take mean while vec_logical are logical values, vec_char are character values and vec_factor are factors values that can't take means.


## Transforming variable type

Tranfoming to numerical variable:
```{r, message = FALSE, warning = FALSE, results = 'hide'}
as.numeric(Prob1_df$vec_logical)
as.numeric(Prob1_df$vec_char)
as.numeric(Prob1_df$vec_factor)
```

Converting character variable from character to factor to numeric:
```{r}
as.factor(Prob1_df$vec_char)
as.numeric(Prob1_df$vec_char)
mean(as.numeric(Prob1_df$vec_char))
class(as.numeric(Prob1_df$vec_char))
```
And the vec_char has been explicitly changed into numerical value that could take mean as "NA", and could be changed into a factor variable

Converting factor variable from factor to character to numeric:
```{r}
as.character(Prob1_df$vec_factor)
as.numeric(Prob1_df$vec_factor)
mean(as.numeric(Prob1_df$vec_factor))
class(as.numeric(Prob1_df$vec_factor))
```
And the vec_factor has been explictly changed into numerical value based on "T" or "F" and could take mean as "1.5", and it could be changed into a factor variable


# Problem 2

## Creating data frame
```{r}
Prob2_df = tibble(
  x = rnorm(1000, mean = 0, sd = 1),
  y = rnorm(1000, mean = 0, sd = 1),
  vec_logical = c(x + y > 0),
  vec_numeric = as.numeric(vec_logical),
  vec_factor = as.factor(vec_logical)
)
```

The size of the dataset is `r nrow(Prob2_df)`, the mean of x is `r mean(Prob2_df$x)`, the median of x is `r median(Prob2_df$x)`, and the proportion of cases for which the logical vector is TRUE is `r table(Prob2_df$vec_logical)["TRUE"]`.

## Make scatterplots

First Scatterplot making color points using the logical variable
```{r}
ggplot(Prob2_df, aes(x = Prob2_df$x, y = Prob2_df$y, color = vec_logical)) + geom_point()
```

Second Scatterplot making color points using the numeric variable
```{r}
ggplot(Prob2_df, aes(x = Prob2_df$x, y = Prob2_df$y, color = vec_numeric)) + geom_point()
```

Third Scatterplot making color points using the factor variable
```{r}
ggplot(Prob2_df, aes(x = Prob2_df$x, y = Prob2_df$y, color = vec_factor)) + geom_point()
```

## Export first scatterplot to current project directory
```{r}
ggsave("1st_scatterplot.png", plot = ggplot(Prob2_df, aes(x = Prob2_df$x, y = Prob2_df$y, color = vec_logical)) + geom_point())
```






