---
title: "p8105_hw1"
author: "Yue Gu"
date: 2018-09-16
output: github_document
---

I'm an R Markdown document! 

# Library
```{r}
library(tidyverse)
```

# Problem 1

1. Here's a random sample of size 10 from a uniform[0,5] distribution,
and I created logical vector, character vector and factor vector as required.

```{r}
## creating data frame
Prob1_df = tibble(
  vec_numeric = runif(10, min = 0, max = 5),
  vec_logical = c(vec_numeric > 2),
  vec_char = c("I", "am", "happy", "to", "take", "the", "data", "science", "course", "today"),
  vec_factor = factor(c("T", "F", "T", "F", "T", "F", "T", "T", "F", "F"))
)

## examine classes
class(Prob1_df$vec_numeric)
class(Prob1_df$vec_logical)
class(Prob1_df$vec_char)
class(Prob1_df$vec_factor)
```

Length of the vector shown below:
  ```{r}
## getting length
length(Prob1_df$vec_char)
length(Prob1_df$vec_factor)
```

2. When taking the mean of each variable, only vec_numeric works since it's the only numerical variable that could have take mean while vec_logical are logical values, vec_char are character values and vec_factor are factors values that can't take means.






